On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-01-18 MS.tex
Small corection

We had no hypotheses about a change in the correlation between trait and growth as AGR was used instead of RGR, except for seed mass. For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping). For other traits, effect size were generally consistent between RGR and AGR when both measurement were available. Some differences occured but they were not easily attributed to any single cause. For instance for WD, the correlation at juvenile stage shifted from negative with RGR to non significant with AGR (i.e CI included zero, Fig. \ref{fig:fig4}b). The correlation coefficients recorded for AGR came from Augspurger & Kelly (1984) and unlike others they used wood density values from adult plants together with growth from juveniles.

>>>>

We had no hypotheses about a change in the correlation between trait and growth as AGR was used instead of RGR, except for seed mass. For seed mass, effects size differed significantly between RGR and AGR at seedling stage; as expected the correlation with RGR was positive and shifted to non significant with AGR (Fig \ref{fig:fig4}d; CI not overlapping). For other traits, effect size were generally consistent between RGR and AGR when both measurement were available. Some differences occured but they were not easily attributed to any single cause. For instance for WD, the correlation at juvenile stage shifted from negative with RGR to non significant with AGR (i.e CI included zero, Fig. \ref{fig:fig4}b). The correlation coefficients recorded for AGR came from \citet{Augspurger:1984ct} and unlike others they used wood density values from adult plants together with growth from juveniles.
